Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-10 paper/main.tex

F12 -> satellite name \\
1995 -> year at start of orbital segment \\
01 -> month at start of orbital segment \\
01 -> day of month at start of orbital segment \\
00 -> hour of day at start of orbital segment \\
14 -> minute of hour at start of orbital segment \\
.night -> orbit is cropped to only nighttime data \\
.OIS -> acronym for OLS Interleaved Smooth \\

@@

@@

@@

    Writing contribution includs: The previous 8 paragraphs of solution summary, and H, I, J, K subsections in it. The A, E, G subsections of proposed solution. The A, C 
    subsections of security Considerations. The section of actual AWS expenditure.

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quited the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank---Light Every Light doucument,and I have done further study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
    Writing part:
    I have wrote the Light Every night part of paper in solution summary. And in proposed solution,I have wrote part of process the data.

>>>>

F12 \-\> satellite name \\
1995 \-\> year at start of orbital segment \\
01 \-\> month at start of orbital segment \\
01 \-\> day of month at start of orbital segment \\
00 \-\> hour of day at start of orbital segment \\
14 \-\> minute of hour at start of orbital segment \\
.night \-\> orbit is cropped to only nighttime data \\
.OIS \-\> acronym for OLS Interleaved Smooth \\

@@

\subsubsection{Step 1. Identify \& Category}

\subsubsection{Step 2. High level: who can access}

\subsubsection{Step 3. Policy from cloud IAM}

\subsubsection{Step 4.what is more}

@@

Totally it spend 70\$. The imagery processing accounted for 50 percent. EC2 accounted 20 percent. RDS accounted 30 percent.

@@

    Writing contribution includs: The previous 8 paragraphs of solution summary, and H, I, J, K subsections in it. The A, E, G subsections of proposed solution. The section of security Considerations. The section of actual AWS expenditure.

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quit the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank---Light Every Light doucument,and I have done further study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
    Writing part:
    I have wrote the Light Every night part of paper in solution summary. And in proposed solution,I have wrote part of process the data.
